\emph{MixFishSim}: highly resolved spatiotemporal simulations for exploring mixed fishery dynamics

### 2019-07-11 write_up/mixfishsim_ecolmod.tex
Additional discussion text

%% Comparison to other models
Typically, simulation models which treat fish as individuals are focussed on
exploring the inter- and intra- specific interactions among fish populations
(e.g. OSMOSE \cite{Shin2004}) in order to understand how they vary over space
and time. Our focus was on understanding how fleets which exploit multiple fish
populations realise catch distributions which may differ from the underlying
populations. As such, we favoured a minimum realistic model of the fish
populations after \cite{Plaganyi2014}, while incorporating fishing dynamics
which take account of different drivers in a mechanistic way, similarly to
other approaches \citep{Fulton2011} but at an individual vessel rather than
fleet level.

@@

Our results demonstrate the importance of data scale and resolution when using
observational data to support management measures. In doing so it highlights
depends on scale of process: pop movement etc... Important to consider how
fishers interact / adapt to changes with the resource and mgmt. \\

%% key findings in context

It seems clear that spatial disaggregation is more important than the temporal
disaggregation of the commercial data... WHY

Closure scenarios demonstrate potential tor reduce F - not as high as with real
pop, but good.  Make link to other studies -- read up on these. \\

@@

\underline{The what next:} \\

Real world spatiotemp closures rarely been able to consider these issues /
designed with these issues fully in mind - NS cod closures, plaice and trevose
box... \\

Use of commercial data increasing - likely to become more important in future.
Also collaborative approach with industry, e.g. hotspot mapping, spatiotemp
advice... \\

Other potential uses of the model \\

Survey design - random, fixed, stratified - all possible to explore  \\

Assumptions in spatiotemporal models: GAMs, GLMMs, geostatistical models

Natural mortality estimation

Commercial index standardization methods - different spatial scales, individual
vessels, data aggregation -- all these can be explored. \\

Sampling scheme design \\

Testing fleet dynamics models at an aggregated level \\

>>>>

%% Comparison to other models
Typically, simulation models which treat fish as individuals are focussed on
exploring the inter- and intra- specific interactions among fish populations
(e.g. OSMOSE \cite{Shin2004}) in order to understand how they vary over space
and time. Our focus was on understanding how fleets which exploit multiple fish
populations realise catch distributions which may differ from the underlying
populations. As such, we favoured a minimum realistic model of the fish
populations after \cite{Plaganyi2014}, while incorporating fishing dynamics
which take account of different drivers in a mechanistic way, similarly to
other approaches \citep{Fulton2011} but at an individual vessel rather than
fleet level. We do not explicitly define fleets as rational profit maximisers
at the outset, but consider there are several stages to development of the
fishery; information gathering through search where the resource location is
not known,  followed by individual learnt behaviour of profitable locations.
This provides a realistic model of how fishing patterns are established and
maintained to exploit an uncertain resource \citep{Mangel1983, Bailey2018}.

@@

Our results demonstrate the importance of considering data scale and resolution
when using observational data to support management measures. We find that
understanding of the community composition dynamics will depend on the level of
data aggregation and that its important to consider the scale of process;
including population movement movement rates, habitat uniformity and fishing
targeting practices if potential biases in data are going to be addressed. Two
contrasting approaches in this respect were the spatial closures to protect cod
in the North Sea. In one example, large scale spatial closures were implemented
with little success due to effort displacement to previously unfished areas
\citep{Dinmore2003}, while in another small scale targeted spatiotemporal
closures were considered to have some effect in reducing cod mortality without
having to disrupt other fisheries significantly \citep{Needle2011}. These
emphasise the importance of considering the right scale and aggregation of data
when identifying area closures.
NOTE: CHECK THIS SECTION, IS A BIT "LOOSE".
\\

%% key findings in context
\subsection{How does data aggregation and source impact on spatial fisheries
	management measures?}

From our simulations spatial disaggregation was more important than the
temporal disaggregation of the commercial data. This reflects the fact that
there was greater spatial heterogeneity over the spatial domain than
experienced in individual locations over the course of the year. This indicates
that fixed closures, if in the right locations, when based on commercially
derived data have the potential to reduced fishing mortality. The likely cost
of poor spatial and temporal resolution is associated with reduced
effectiveness and potentially closing fishing opportunities for other
fisheries. Our study showed that fishing rates on other populations also
changed (both up and down) as a side-effect of closures to protect one species.
This indicates the importance in considering fishing effort reallocation
following spatial closures, and our simulation allows us to consider the
spatiotemporal reasons for these changes.

We model the population and fleet dynamic processes in order to draw inference
on the importance of data scale and aggregation in understanding and managing
mixed fisheries and their impact on multiple fish populations. In doing so, we
have necessarily had to make a number of simplifying assumptions. \\

Fish populations in our simulations move in pre-defined timescales and
according to fixed habitat preferences and temperature gradients. Our
assumptions in parametrising the model (movement rates, temperature tolerances)
will have a direct impact on our conclusions on the relative importance of
spatial and temporal processes. These assumptions could be explored in a future
study by varying the parameters and assessing the robustness of our
conclusions. \\

In addition, we have assumed that fishing vessels are not restricted by quota
and therefore discarding of species for which vessels have no quota or which
are unwanted is not taken into account. This is likely to be a significant
source of bias in any inference using commercial data and should also be
explored. \\

@@

We consider that the increased availability of high resolution catch and
locational information from commercial fisheries will require it to be a key
source of data for ensuring management is implemented at the right scale in
future. For example, identifying hot-spots for bycatch reduction or identifying
spatial overlaps in mixed fisheries \citep{Dolder2018, Gardner2008, Little2014,
	Dedman2015, Ward2015}. Our simulation model has the potential to test
some of the assumptions behind the modelling approaches in identifying such
hotspots and indeed behind spatiotemporal modelling in general (e.g. comparing
GAMs, GLMMs, Random Forests and geostatistical models under different data
generation processes as exampled by \cite{Stock2019}). \\

Other novel applications of our framework could be; testing different survey
designs given multiple species and data generating assumptions; commercial
index standardisation methods and approaches and understanding of appropriate
scales and data aggregations; exploring assumptions about the distribution of
natural mortality and fishing mortality throughout the year and importance of
capturing in-year dynamics in estimating stock status; at sea sampling scheme
designs to deliver unbiased estimates of population parameters; testing the
ability of commonly employed fleet dynamics models such as Random Utility
Models to capture finescale dynamics and understand their importance. \\
